### 2016-09-23 comparison_with_mma.tex
Use CAS's (reviewer 3 comment 3)
Fix failing Matrix doctest

While Mathematica interprets nested lists as matrices whenever
the sublists have the same length, matrices in SymPy are a type in their own
right, allowing ordinary operators and functions (like multiplication and
exponentiation) to be used as they traditionally are in mathematics.
\begin{verbatim}
>>> exp(Matrix([[1, 1],[0, 2]])) * Matrix([a, b])
Matrix([
[E*a + b*(-E + exp(2))],
[             b*exp(2)]])
\end{verbatim}

@@

SymPy's use of floating-point numbers is similar to that of most
other CASes, including Maple and Maxima.
By contrast, Mathematica uses a form
of significance arithmetic~\cite{Sofroniou2005precise} for approximate numbers.
This offers further protection against numerical errors,
although it comes with its own set of problems
(for a critique of significance arithmetic, see Fateman~\cite{Fateman1992}).
Internally, SymPy's \texttt{evalf} method works similarly to Mathematica's
significance arithmetic, but the semantics are isolated from the rest of the system.

>>>>

While Mathematica interprets nested lists as matrices whenever
the sublists have the same length, matrices in SymPy are a type in their own
right, allowing ordinary operators and functions (like multiplication and
exponentiation) to be used as they traditionally are in mathematics.
\begin{verbatim}
>>> a, b = symbols('a b')
>>> exp(Matrix([[1, 1], [0, 2]])) * Matrix([a, b])
Matrix([
[E*a + b*(-E + exp(2))],
[             b*exp(2)]])
\end{verbatim}

@@

SymPy's use of floating-point numbers is similar to that of most
other CAS's, including Maple and Maxima.
By contrast, Mathematica uses a form
of significance arithmetic~\cite{Sofroniou2005precise} for approximate numbers.
This offers further protection against numerical errors,
although it comes with its own set of problems
(for a critique of significance arithmetic, see Fateman~\cite{Fateman1992}).
Internally, SymPy's \texttt{evalf} method works similarly to Mathematica's
significance arithmetic, but the semantics are isolated from the rest of the system.
